The Concurrent Calculi Formalisation Benchmark

### 2024-02-01 short-paper/short-paper.tex
minor edits for style

As with the POPLMark and POPLMark Reloaded challenges, this challenge does not aim to cover every possible
problem in the area. Our benchmark can be extended in two
dimensions: further expanding and combining the current challenges,
and addressing features not covered by the current challenges.

@@

\vspace{-1mm}%
\paragraph{Addressing new calculi and new features.}
Extending in this direction
means proposing new challenges covering different features of
process calculi, or different proof mechanisation features.
Some interesting aspects of message-passing calculi to be explored in
further challenges could be multiparty session types and
choreographies, as their meta-theory includes aspects -- \eg, well-formedness conditions on global types, partiality of end-point projection function, etc. --
that we do not cover here. Also, one could easily
design a challenge that goes beyond our coinduction challenge, by
exploring different notions of bisimilarity (barbed, weak, \etc)
and trace equivalence.
%
\luca{Coinduction may also play a relevant role in supporting recursive
processes and session types. Indeed, it is often the case that session type
systems (and logics) with recursive session types (and propositions) are
naturally expressed in \emph{infinitary form} by interpreting their typing (and
proof) rules coinductively. I CAN ADD ONE OR TWO REFERENCES IF YOU FEEL IT'S APPROPRIATE}

>>>>

Similar to the POPLMark and its Reloaded counterpart, this challenge
does not encompass all potential problems in the field. Our benchmark
is extendable in two aspects: it can further amalgamate and broaden
the existing challenges, and tackle aspects not yet covered by them.

% As with the POPLMark and POPLMark Reloaded challenges, this challenge does not aim to cover every possible
% problem in the area. Our benchmark can be extended in two
% dimensions: further expanding and combining the current challenges,
% and addressing features not covered by the current challenges.

@@

\vspace{-1mm}%
\paragraph{Addressing new calculi and new features.}
Extending in this direction
means proposing new challenges covering different features of
process calculi, or different proof mechanisation features.
Some interesting aspects of message-passing calculi to be explored in
further challenges could be multiparty session types and
choreographies, as their meta-theory includes aspects -- \eg, well-formedness conditions on global types, partiality of end-point projection function, etc. --
that we do not address here. Also, one could easily
design a challenge that goes beyond our coinduction challenge, by
exploring different notions of bisimilarity (barbed, weak, \etc)
and trace equivalence.
%
\luca{Coinduction may also play a relevant role in supporting recursive
processes and session types. Indeed, it is often the case that session type
systems (and logics) with recursive session types (and propositions) are
naturally expressed in \emph{infinitary form} by interpreting their typing (and
proof) rules coinductively. I CAN ADD ONE OR TWO REFERENCES IF YOU FEEL IT'S APPROPRIATE}
